### 2011-02-10 paper/hyperNeatMethod.tex
shrink
foo
minor + shrink

\subsection{HyperNEAT Gait Generation and Learning}
\seclabel{hyperNeatMethod}

@@

\acmFig{hyperneatExplanation.png}{1}{HyperNEAT Produces ANNs from
  CPPNs. ANN weights are specified as a function of the geometric
  coordinates of the source node and the target node for each
  connection. The coordinates of these nodes and a constant bias are
  iteratively passed to the CPPN to determine each connection
  weight. The CPPN has two output values, which specify the weights
  for each connection layer as shown.}

@@

\acmFig{SpiderANN.jpg}{1}{ANN Configuration for HyperNEAT Runs. The
  first two columns of each row of the input layer receive information
  about a single leg (the current angle of its two joints). The final
  column provides a sine and cosine wave to enable periodic movements
  and the angle of the center joint. Evolution determines the function
  of the hidden-layer nodes. The nodes in the output layer specify new
  joint angles for each respective joint. The unlabeled nodes in the
  input and output layers are ignored.}\label{hyperneatLayout}

As with the parameterized learning methods, three runs of HyperNEAT
were performed. The population size for HyperNEAT was 9 and runs
lasted 20 generations. These numbers are small, but were necessarily
constrained given how much time it took to conduct evolution directly
on a real robot. The remaining parameters were identical to Clune et
al.~\cite{clune2011performance}.

>>>>

\subsection{HyperNEAT Gait Generation \& Learning}
\seclabel{hyperNeatMethod}

@@

\acmFig{hyperneatExplanation.png}{.8}{HyperNEAT produces ANNs from
  CPPNs. ANN weights are specified as a function of the geometric
  coordinates of the source node and the target node for each
  connection. The coordinates of these nodes and a constant bias are
  iteratively passed to the CPPN to determine each connection
  weight. The CPPN has two output values, which specify the weights
  for each connection layer as shown.}

@@

\acmFig{SpiderANN.jpg}{.7}{ANN configuration for HyperNEAT Runs. The
  first two columns of each row of the input layer receive information
  about a single leg (the current angle of its two joints). The final
  column provides a sine and cosine wave to enable periodic movements
  and the angle of the center joint. Evolution determines the function
  of the hidden-layer nodes. The nodes in the output layer specify new
  joint angles for each respective joint. The unlabeled nodes in the
  input and output layers are ignored.}\label{hyperneatLayout}

As with the parameterized methods, three runs of HyperNEAT
were performed. The population size for HyperNEAT was 9 and runs
lasted 20 generations. These numbers are small, but were necessarily
constrained given how much time it took to conduct evolution directly
on a real robot. The remaining parameters were identical to Clune et
al.~\cite{clune2011performance}.
